A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-24 src/tex/ms.tex

\begin{figure}
    \centering
    \includegraphics{figures/abundance_evolution_yields.pdf}
    \caption{Caption.}
    \label{fig:abund-evol-yields}
\end{figure}

>>>>

\begin{figure*}
    \centering
    \includegraphics{figures/abundance_evolution.pdf}
    \caption{Stellar age--abundance relations produced by select multi-zone models. Each point represents a stellar population drawn from the Solar neighborhood near the mid-plane ($7\leq R_{\rm gal}\leq 9$ kpc, $0\leq |z| \leq 0.5$ kpc) and is color-coded by its birth radius. For visual clarity, we plot a only random mass-weighted sample of \num{10000} points in each panel. The dashed line plots the ISM abundance at $R_{\rm gal}=8$ kpc over time. The black points plot the median abundance of stars in 2 Gyr-wide age bins, and the vertical error bars represent the 16th and 84th percentiles of the age distribution. Similarly, the red points with error bars plot the median APOGEE abundances for stars with age estimates from \citet{leung_variational_2023}. Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model, with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7$ kpc, and pristine gas infall; {\bf (b)} a model with higher yields $y/Z_\odot=2$; {\bf (c)} a model with greater radial migration strength $\sigma_{\rm RM8}=5$ kpc; and {\bf (d)} a model which assumes the infalling gas has metallicity ${\rm [O/H]}_{\rm CGM}={\rm [Fe/H]}_{\rm CGM}=-0.7$. {\bf Key takeaway:} the fiducial model shows two discrepancies with the data: a major dilution event at a lookback time of $\sim9$ Gyr and non-zero abundance evolution at late times. Only model (b) with higher yields can mitigate both of these issues.}
    \label{fig:abundance-evolution}
\end{figure*}
